### 2018-05-05 papers/synth/example.tex
final graph
asd
sad

% \newenvironment{psmallmatrix}
%   {\left(\begin{smallmatrix}}
%   {\end{smallmatrix}\right)}

\begin{figure}[t]
  \centering
  \begin{tikzpicture}[->,>=stealth',auto,node distance=5cm,
  thick,main node/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
  \node[main node,text width=3cm] (ga) {GA{\small \^{Qa4} \^{Qa6} \^{Qb4} \^{Qb6} \^{Qc4} \^{R6}}};
  \node[main node] (ic) [below right of=ga,yshift=20mm,xshift=20mm] {IC {\small \^{Qa6} \^{Qb6} \^{R1}}};
  \node[main node] (er) [below right of=ga] {ER {\small \^{Qa1} \^{Qb1} \^{R1}}};
  \node[main node,text width=2.5cm] (pm) [above right of=ga] {PM {\small \^{Qa5} \^{Qa7} \^{Qbc2} \^{Qbc7}}};
  \node[main node] (ee) [below right of=pm] {EE {\small \^{Qa2} \^{Qb2/3} \^{Qc2/3}}};
  \node[main node] (le) [above of=ee,yshift=-13mm,xshift=18mm] {LE {\small \^{Qa8} \^{Qb8} \^{Qc8}}};

  \path (ic) edge node [below] {\^{Qc6}} (ga);
  \path (er) edge[bend right=20] node [right] {\^{Qc6}} (ic);

  %er <> ga
  \path (er) edge[bend right=20] node [left] {\^{Qc6}} (ga);
  \path (er) edge[bend left=20] node [left] {R6} (ga);
  \path (ga) edge[bend right=40] node [left] {\^{Qc1}} (er);

  %ga <-> ee
  \path (ga) edge[bend left=25] node [above] {Qb2 Qc2} (ee);
  \path (ga) edge[bend left=10] node [above] {Qbc2/3} (ee);
  \path (ee) edge[bend left=0] node [below] {Qb2/3,Qa2,R2,\^{R4},Qc2/3} (ga);

  %le <-> pm
  \path (le) edge[bend right=10] node [above] {Qb7 Qc7} (pm);
  %ee -> le
  \path (ee) edge[bend right] node [below,rotate=70] {\^{R8},Qa7,Qbc7,R7} (le);

  %pm <-> ee
  \path (ee) edge[bend left=10] node [above] {\^{R3}} (pm);
  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);

  %ga->pm
  \path (ga) edge[bend left=10] node [right] {{Qb2} Qc2} (pm);
  \path (ga) edge[bend left=80] node [above] {\^{R2}} (pm);
  \path (ga) edge[bend left=52] node [above] {\^{R7}} (pm);
  \path (ga) edge[bend left] node [above] {\^{R8}} (pm);
  \end{tikzpicture}
  \caption{found-in-nature VTS}
  \label{fig:mukund-vts}
\end{figure}

%t snares are labelled within compartmetns, v snares on the edges
%and snare complexes on the left-hand side
The figure~\ref{fig:mukund-vts} represent mammalian SNARE map created by studying the references~\cite{somya}. 
To construct the map, we have assumed that vesicles only contain a single
active v-SNARE, and we have attributed t-SNAREs and inactive v-SNAREs that
travel between compartments to one of the known vesicles that go between
the same source and target compartments.
In order to identify the active SNARE complex involved in any particular
vesicle fusion, two criteria were used: 
\begin{enumerate}
\item[a.] The SNARE complex is formed \textit{in vivo}. In most papers, this is determined by immunoprecipitation of the SNARE complex from the relevant cell fraction. 
\item[b.] Blocking SNARE complex formation (for example, using antibodies against these SNAREs, or
using cytosolic forms of these SNAREs) blocks the specific transport step.
\end{enumerate}

Note that these vesicles have been collected from multiple cell types, and
any given cell type is likely to contain only a subset of the vesicles in
the map.

In this diagram the gray circles represent compartments, the identities of compartments are
written within: ER=endoplasmic reticulum, ERGIC=ER-Golgi intermediate compartment,
RE=recycling endosome, EE=early endosome, LE=late endosome, LYS=lysosome, PM=plasma
membrane. Thin black arrows represent vesicle edges.
% and hollow arrows represent maturation edges. 
The set of SNAREs contained in these edges are written alongside each edge. Actual names
of these SNAREs are mentioned in the key alongside. The red labels represent the paths taken by
SNARES of the complex Stx-4-SNAP23-VAMP7. Here, the cycles for two SNARE molecules,
VAMP7 and SNAP23 are complete. The green labels represent the paths taken by SNAREs of the
complex Stx13-SNAP25-VAMP2. Here the cycle for VAMP2 is complete.The blue labels represent
the paths taken by SNARES of the complex Stx5-Gs28-Bet1/GS15-Ykt6. Here, cycles for none of
the SNAREs are complete. So, even though most edges known so far are present in the map, paths for molecules (SNAREs) across the cell are still not complete.

>>>>

\input{fig-mukund-vts}

In figure~\ref{fig:mukund-vts}, we present the VTS for mammalian cells
obtained by studying the literature.
%
The

% and hollow arrows represent maturation edges.
